\relike: Reionization Effective Likelihood from Planck 2018 Data

### 2021-04-28 paper/rei.tex
Updates from Overleaf

Many probes of  the reionization era exist today and with future probes it will only become more important to combine them consistently the full implications of the CMB. In the CMB data, free electrons during the reionization epoch Compton scatter with the CMB photons to cause a suppression of the CMB primary anisotropies; on the large scales, the same scattering process of the CMB temperature quadrupole in the frame of the free electrons induces an additional reionization bump in the CMB $E$-mode polarization. On the small scales, the kinetic Sunyaev-Zeldovich (kSZ) effects generated by the scattering of the CMB photons off ionized gas in bulk motion~\cite{zeldovich_sunyaev_1969, sunyaev_zeldovich_1980} are used to constrain morphology and duration of reionization~\cite{mcquinn_2005,mesinger_2012_kSZ}. Additionally, observations of galaxy luminosity functions, quasars, star formation rate, line-intensity mapping also provide important and complementary information on reionization~\cite{2016ASSL..423.....M}. In this paper, we aim to extract all the information in the large-scale $E$-mode observations for constraining the global ionization history of the Universe, and provide a way to consistently analyze them with all of these other probes.

>>>>

Many probes of  the reionization era exist today and with future probes it will only become more important to combine them consistently the full implications of the CMB. In the CMB data, free electrons during the reionization epoch Compton scatter with the CMB photons to cause a suppression of the CMB primary anisotropies; on the large scales, the same scattering process of the CMB temperature quadrupole in the frame of the free electrons induces an additional reionization bump in the CMB $E$-mode polarization. On the small scales, the kinetic Sunyaev-Zeldovich (kSZ) effects generated by the scattering of the CMB photons off ionized gas in bulk motion~\cite{Sunyaev:1970er, Sunyaev:1980vz} are used to constrain morphology and duration of reionization~\cite{mcquinn_2005,mesinger_2012_kSZ}. Additionally, observations of galaxy luminosity functions, quasars, star formation rate, line-intensity mapping also provide important and complementary information on reionization~\cite{2016ASSL..423.....M}. In this paper, we aim to extract all the information in the large-scale $E$-mode observations for constraining the global ionization history of the Universe, and provide a way to consistently analyze them with all of these other probes.
